Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-11-26 manuscript.Rmd
updates

```{r setup, include=FALSE}
library(tidyverse)
library(sf)
library(rgdal)
library(tigris)
library(spdep)

#tigris package - contains roads for DC
options(tigris_class="sf")

@@

#primary_secondary_roads includes interstates and other highways in DC
dc_roads <- primary_secondary_roads(state="DC") %>%
	st_transform(crs = 102285)
```

@@

According to the New York Times, crowd scientists estimated 470,000 people were at the women’s march in Washington on January 21st, 2017. They say that the crowd at the women’s march was about three times the size of the crowd at the Trump inauguration, making the crowd roughly 160,000 people at the Trump inauguration. 
https://www.nytimes.com/interactive/2017/01/22/us/politics/womens-march-trump-crowd-estimates.html

```{r join_sf}
dc_census <- st_read("data/uber_dc_tracts.json") %>%
	select("id" = MOVEMENT_ID, geometry) %>%
	mutate(id = factor(id, levels = levels(travel_times$dest_id)))

travel_time_sf <- left_join(x = travel_times, y = dc_census, by = c("dest_id" = "id")) %>%
	st_as_sf() %>%
	st_transform(crs = 102285)
```

```{r map}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3) %>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	theme_map +
	scale_fill_viridis_c(direction = -1)

travel_time_sf %>% filter(year == 2017, month == 1, week == 4)%>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	geom_sf(data = dc_roads) +
	theme_map +
	scale_fill_viridis_c(direction = -1)
```

```{r}
mean((travel_times %>% filter(year == 2017, month == 1, week == 3))$mean_travel_time)
```

```{r}
mean((travel_times %>% filter(year == 2016, month == 9, week == 3))$mean_travel_time)
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(sf)
library(rgdal)

@@

head(travel_times)
```

```{r}
demographic_data_big <- read.csv("DC_demographic_data.csv", header = FALSE)
names <- unlist(demographic_data_big[2,])
demographic_data_big <- demographic_data_big %>% 
  slice(3:8096)
head(demographic_data_big)
colnames(demographic_data_big) <- names
demographic_data_big <- demographic_data_big %>% 
  mutate(state = substr(geo2010, start = 1, stop = 2)) %>% 
  mutate(tract_number = substr(geo2010, start = 10, stop = 1000))
head(demographic_data_big)

```

```{r}
#Attempting to add roads in this code chunk

library(spdep)
library(sf)
roads<-st_read("dc_roads")
#row.names(roads) <- as.character(roads$FIPSNO)
#plot(st_geometry(roads), axes=TRUE)

#tigris package - contains roads for DC
options(tigris_class="sf")
#primary_secondary_roads includes interstates and other highways in DC
dc <- tigris::primary_secondary_roads(state="DC")
dc
plot(dc)
```

@@

According to the New York Times, crowd scientists estimated 470,000 people were at the women’s march in Washington on January 21st, 2017. They say that the crowd at the women’s march was about three times the size of the crowd at the Trump inauguration, making the crowd roughly 160,000 people at the Trump inauguration. 
https://www.nytimes.com/interactive/2017/01/22/us/politics/womens-march-trump-crowd-estimates.html
The 2010 data set of demographic information by census tracts comes from Urban Institute: https://greaterdc.urban.org/data-explorer?geography=tr10&indicator=PctBlackNonHispBridge&topic=population&year=2012-16

```{r join_sf}
DC_census <- st_read("data/washington_DC_censustracts.json") %>%
	select("id" = MOVEMENT_ID, geometry) %>%
	mutate(id = factor(id, levels = levels(travel_times$dest_id)))

DC_census

travel_time_sf <- left_join(x = travel_times, y = DC_census, by = c("dest_id" = "id")) %>%
	st_as_sf() %>%
	st_transform(crs = 102285)

st_centroid(x = travel_time_sf)
```

```{r map}
travel_time_sf %>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	theme_map +
	scale_fill_viridis_c(direction = -1)
```

```{r}
travel_time_sf %>% filter(year == 2017, month == 1, week == 3)%>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	theme_map +
	scale_fill_viridis_c(direction = -1)

travel_time_sf %>% filter(year == 2017, month == 1, week == 4)%>%
	ggplot() +
	geom_sf(mapping = aes(fill = mean_travel_time)) +
	theme_map +
	scale_fill_viridis_c(direction = -1)
```
